Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-30 paper-filmat.tex
One more comment (in response to review)

Just as the \effective topos provides a coherent setting for studying
computability using a naive language, the sheaf topos~$\Sh(X)$ provides a
coherent setting for studying continuous~$X$-indexed families of objects (sets,
numbers, functions) as if they were single objects.
% FUTURE: Explain better.
% FUTURE: History, sites, flexibility

>>>>

Just as the \effective topos provides a coherent setting for studying
computability using a naive element-based language, the sheaf topos~$\Sh(X)$ provides a
coherent setting for studying continuous~$X$-indexed families of objects (sets,
numbers, functions) as if they were single objects.

Sheaf toposes take up a special place in the history of topos theory: If the
base~$X$ is allowed to be a \emph{site} instead of a topological space, the
resulting toposes constitute the large class of Grothendieck toposes, the
original notion of toposes. Categorically, the passage from topological spaces
to sites is rather small, but the resulting increase in flexibility is
substantial and fundamental to modern algebraic geometry.
